Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-03-06 sections/acknowledgements.tex

% Come back and indent and make parentheses affiliations
\begin{enumerate}
    \item Scott Austin, Ph.D. (Director of Astronomical Facilities Associate Professor of Astronomy and Physics, Department of Physics, Astronomy, and Engineering, University of Central Arkansas) 
    \item Todd Abel, Ph.D. (UCA STEM Institute Co-Director, Associate Professor of Mathematics, Secondary Mathematics Education Program Coordinator)
    \item Shane Ayotte. (UCA Mathematics Student)
\end{enumerate}

>>>>

% Come back and indent and make parentheses affiliations
\begin{enumerate}
    \item Scott Austin, Ph.D. (Director of Astronomical Facilities, Associate Professor of Astronomy and Physics, Department of Physics, Astronomy, and Engineering, University of Central Arkansas) 
    \item Todd Abel, Ph.D. (UCA STEM Institute Co-Director, Associate Professor of Mathematics, Secondary Mathematics Education Program Coordinator)
    \item Shane Ayotte. (UCA Mathematics Student)
\end{enumerate}
